Replication on multicore considering hierarchy and characteristics of the network

### 2013-04-27 paper.tex
Program to evaluate model The current version seems to properly calculate cost for sending a broadcast along the 'gruyere' tree

>>>>

There are two problems:
\begin{enumerate}
\item Performance of distributed algorithms on multicores. Programmers
  don't get it right due to different complexity measures. We deal
  with this by improving these algorithms. This will lead to higher
  performance of existing algorithms.
\item Diversity of hardware. Hand-tuning algorithms is tedious. Need
  to do this automatically. To evaluate this, we compare the average
  performance of our automatic configuration on a wide range of
  multicores with performance of a single hand-tuned implementation.
\end{enumerate}
